### 2022-06-03 msp/testy/testy.tex
MSP fix

    \item Doplněk kritického oboru pro alternativní hypotézu ${\displaystyle H_{A}}$:
    $${\displaystyle \qquad \overline{W_\alpha} = \big\langle -t_{1 - \frac{\alpha}{2}}(k) ~,~ t_{1 - \frac{\alpha}{2}}(k) \big\rangle \approx \big\langle 2.0096 ~,~ 2.0096 \big\rangle}$$

>>>>

    \item Doplněk kritického oboru pro alternativní hypotézu ${\displaystyle H_{A}}$:
    $${\displaystyle \qquad \overline{W_\alpha} = \big\langle -t_{1 - \frac{\alpha}{2}}(k) ~,~ t_{1 - \frac{\alpha}{2}}(k) \big\rangle \approx \big\langle -2.0096 ~,~ 2.0096 \big\rangle}$$
